External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising

### 2016-10-26 CVPR2017_Review_Unified.tex
add

\subsection{External Patch Group Prior Learning}
Natural images often demonstrate repepitive patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm,pgpd} and restoration methods \cite{}. In \cite{pgpd}, the NSS property is directly learned as an external prior in a patch group manner. In this section, we formulate the Patch Group prior on natural color images.

In \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch. The patch group mean is destracted, and hence different groups patches can share similar PGs. Therefore the space to be modeled is largely reduced. In this work, we extract PGs from RGB images. Each patch is of size $p\times p \times 3$. For each local patch, we search its similar patches around it through the Euclidean distance in a local window of size $W\times W$. The PG is denoted by $\{\mathbf{x}_{m}\}_{m=1}^{M}$, where $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a color image patch vector. The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and $\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}$ is the group mean subtracted patch vector. The PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}\}, m=1,...,M$, and it represent the external NSS prior on color images. Assume we have extracted $N$ PGs from a given set of natural images, and the $n$-th PG is defined as $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$. We employ the patch group based Gaussian Mixture Model (PG-GMM) for NSS prior learning. We aim to learn a set of $K$ Gaussians $\{\mathcal{N}(\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})\}$ from $N$ training PGs $\{\mathbf{\overline{X}}_{n}\}$, while requiring that all the $M$ patches $\{\mathbf{\overline{x}}_{n,m}\}$  in PG $\mathbf{\overline{X}}_{n}$ belong to the same Gaussian component and assume that the patches in the PG are independently sampled. Note that such an assumption is commonly used in patch based image modeling \cite{ksvd,lssc}. Then, the likelihood of $\{\mathbf{\overline{X}}_{n}\}$ can be calculated as
\begin{equation}\label{equ1}
P(\mathbf{\overline{X}}_{n})  = \sum\nolimits_{k=1}^{K}\pi_{k}\prod\nolimits_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k}).
\end{equation}
By assuming that all the PGs are independently sampled, the overall objective log-likelihood function is
\begin{equation}\label{equ2}
\begin{split}
\ln\mathcal{L}=\sum_{n=1}^{N} \ln(\sum_{k=1}^{K}\pi_{k}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})).
\end{split}
\end{equation} 
We maximize the above objective function for PG-GMM learning and  finally obtain the GMM model with learned parameters including mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}=\mathbf{0}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$. Noted that the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.

>>>>

\subsection{External Patch Group Prior Learning}
Natural images often demonstrate repepitive local patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm,pgpd}. In this section, we formulate the Patch Group prior learned on natural color images. Similar to \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch. The patch group mean is destracted, and hence different groups patches can share similar PGs. In this way, the space natural image patches to be modeled is largely reduced. In this work, each local patch extracted from RGB images is of size $p\times p \times 3$. Then we search the $M$ most similar patches $\{\mathbf{x}_{m}\}_{m=1}^{M}$ around each local patch through Euclidean distance, in a local window of size $W\times W$. The $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a patch vector formed by combining the 3 patch vectors (of size $p^{2}\times 1$) in R, G, B channels. The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}\}, m=1,...,M$. Assume we have extracted $N$ PGs from a set of external natural images, and the $n$-th PG is defined as $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$. We employ the Gaussian Mixture Model (GMM) to learn the external patch group based NSS prior. In this model, the likelihood of the $n$-th PG $\{\mathbf{\overline{X}}_{n}\}$ can be calculated as
\vspace{-2mm}
\begin{equation}\label{equ1}\vspace{-2mm}
P(\mathbf{\overline{X}}_{n})  = \sum\nolimits_{k=1}^{K}\pi_{k}\prod\nolimits_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k}),
\end{equation}
where $K$ is the number of Gaussians and the $k$-th Gaussian is $\{\mathcal{N}(\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})\}$. By assuming that all the PGs are independently sampled, the overall objective log-likelihood function is
\vspace{-2mm}
\begin{equation}\label{equ2}\vspace{-2mm}
\begin{split}
\ln\mathcal{L}=\sum_{n=1}^{N} \ln(\sum_{k=1}^{K}\pi_{k}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})).
\end{split}
\end{equation} 
We maximize the above objective function for PG-GMM learning and  finally obtain the GMM model with learned parameters including mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}=\mathbf{0}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$. Noted that the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
